Automating Verification of MPC Security

### 2023-06-07 popl24/hyperprop.tex
checkpoint

\section{Hyperproperties}

@@

\example{Example: Additive Secret Sharing} A nice ``Hello World''
example of an MPC protocol is additive secret sharing, where $k$
parties split up their secrets into \emph{shares}, with the property
that all $k$ shares are required to reconstruct the secret and any
fewer reveals nothing. In $\fedcat$, we can use $\ttt{xor}$, again, to
generate shares. Here, party 1 generates 3 shares of the secret
$\sx{1}{1}$- one is given to party 2 through view $\vx{2}{s1}$, one is
given to party 3 through view $\vx{3}{s1}$, and party 1 keeps
$\fx{1}{s1}$ for itself:
\begin{verbatimtab}
v[2,s1] := flip[1,1] xor flip[1,s1] xor s[1,1];
v[3,s1] := flip[1,1];
\end{verbatimtab}
Note that $\vx{2}{s1}$ and $\vx{3}{s1}$ are both in uniform
random distributions.

Another property of $\ttt{xor}$ is that it is additively homomorphic,
while functioning as addition in the boolean algebra (i.e., the binary
field). That is, given:
\begin{mathpar}
  x_1\ \ttt{xor}\ y_1 = z_1

  x_2\ \ttt{xor}\ y_2 = z_2
\end{mathpar}
then we have:
$$
(x_1\ \ttt{xor}\ x_2)\ \ttt{xor}\ (y_1\ \ttt{xor}\ y_2) = z_1\ \ttt{xor}\ z_2
$$
Thus, we can obtain secret 3-party summation (xor) by continuing
the protocol begun above- parties 2 and 3 can share their secrets
in the same fashion:
\begin{verbatimtab}
v[1,s2] := flip[2,1] xor flip[2,s2] xor s[2,1];
v[3,s2] := flip[2,1];

v[1,s3] := flip[3,1] xor flip[3,s3] xor s[3,1];
v[2,s3] := flip[3,1];
\end{verbatimtab}
Then, assuming that party 0 is the ``public party'', each party sums
its own shares, and then the sum of sum of shares is revealed
in the output view $\vx{0}{output}$. By additive homomorphism of
$\ttt{xor}$, this output is the sum of the 3 secrets, but
the protocol reveals nothing to the adversary, even if one
(or even two, in fact) of $\{1,2,3\}$ are corrupt. 
\begin{verbatimtab}
v[0,ss1] := v[1,s2] xor v[1,s3] xor flip[1,s1];
v[0,ss2] := v[2,s1] xor v[2,s3] xor flip[2,s2];
v[0,ss3] := v[3,s1] xor v[3,s2] xor flip[3,s3];

v[0,output] := v[0,ss1] xor v[0,ss2] xor v[0,ss3]
\end{verbatimtab}

Because this protocol correctly implements 3-party addition in the
binary field, it can reveal information to the adversary. For example,
suppose that $1 \in C$, and $\sx{1}{1}$ is $1$, and after running the
protocol suppose that $\vx{0}{output}$ is 0. Then the adversary knows
that 2 and 3's secrets are either 1 and 0, or 0 and 1, with 50/50
probability, and definitely neither 0 and 0, nor 1 and 1. However, the
protocol does not reveal anything more through adversarial views than
what the output reveals.

\medskip

>>>>

\section{Hyperproperties of MPC Passive Security}

@@

### 2023-06-07 popl24/minicat.tex
checkpoint

Expressions forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$ which is essentiall a conditional
expression with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}

\begin{verbatimtab}
v[2, rd] := select[flip[2, d], H[r1], H[r0]];
v[1, e] := s[2, c] xor flip[2, d];
v[2, f0] := s[1, m0] xor select[v[1, e], H[r1], H[r0]];
v[2, f1] := s[1, m1] xor select[not v[1, e], H[r1], H[r0]];
v[2, mc] := (select[s[2, c], v[2, f1], v[2, f0]] xor v[2, rd])
\end{verbatimtab}

>>>>

Expressions forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$ which is essentially a conditional
expression with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

\begin{example}[One-Time Pad]
  \label{example-otp}
We can model secure communication between two parties
using symmetric key encryption over an insecure channel, for
example. In the following program, we assume $H = \{ 1,2 \}$ and
$C = \{ 0 \}$. Party 1 first shares the randomly generated
key $\fx{1}{0}$ with party 2. Then, party 1 encrypts
its secret $\sx{1}{0}$ and sends it to party 0,
which relays the ciphertext in $\vx{0}{0}$ to
party 2. Finally, party 2 decrypts\footnote{Recall we are using
a random tape approach, so the value of $\fx{1}{0}$ remains
consistent during any run the program, though that value
is randomly determined by the initial memory in a given
run} the ciphertext and stores the plaintext in $\vx{2}{2}$. 
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
This protocol is \emph{correct} because $\vx{2}{2}$ is exactly
correlated with the secret $\sx{1}{0}$, and it is \emph{secure}
because the corrupt view $\vx{0}{0}$ in isolation is probabilistically
independent of the secret $\sx{1}{0}$, while serving as a
communication channel for its encryption. 
\end{example}

\begin{example}[Lambda-obliv]
  \label{example-lambda-obliv}

  \begin{verbatimtab}
v[0,0] := select(s[1,0], flip[1,0], flip[1,1] );
v[0,1] := flip[1,0]
\end{verbatimtab}

\begin{verbatimtab}
v[0,0] := select(s[1,0],select(flip[1,0], flip[1,0], flip[1,1]),flip[1,2])
\end{verbatimtab}
\end{example}

\begin{example}[Oblivious Transfer]
  \label{example-lambda-OT}

\begin{verbatimtab}
v[2, rd] := select[flip[2, d], H[r1], H[r0]];
v[1, e] := s[2, c] xor flip[2, d];
v[2, f0] := s[1, m0] xor select[v[1, e], H[r1], H[r0]];
v[2, f1] := s[1, m1] xor select[not v[1, e], H[r1], H[r0]];
v[2, mc] := (select[s[2, c], v[2, f1], v[2, f0]] xor v[2, rd])
\end{verbatimtab}
\end{example}

\begin{example}[Additive Secret Sharing]
    \label{example-lambda-he}
Another 
example of an MPC protocol is additive secret sharing, where $k$
parties split up their secrets into \emph{shares}, with the property
that all $k$ shares are required to reconstruct the secret and any
fewer reveals nothing. In $\fedcat$, we can use $\ttt{xor}$, again, to
generate shares. Here, party 1 generates 3 shares of the secret
$\sx{1}{1}$- one is given to party 2 through view $\vx{2}{s1}$, one is
given to party 3 through view $\vx{3}{s1}$, and party 1 keeps
$\fx{1}{s1}$ for itself:
\begin{verbatimtab}
v[2,s1] := flip[1,1] xor flip[1,s1] xor s[1,1];
v[3,s1] := flip[1,1];
\end{verbatimtab}
Note that $\vx{2}{s1}$ and $\vx{3}{s1}$ are both in uniform
random distributions.

Another property of $\ttt{xor}$ is that it is additively homomorphic,
while functioning as addition in the boolean algebra (i.e., the binary
field). That is, given:
\begin{mathpar}
  x_1\ \ttt{xor}\ y_1 = z_1

  x_2\ \ttt{xor}\ y_2 = z_2
\end{mathpar}
then we have:
$$
(x_1\ \ttt{xor}\ x_2)\ \ttt{xor}\ (y_1\ \ttt{xor}\ y_2) = z_1\ \ttt{xor}\ z_2
$$
Thus, we can obtain secret 3-party summation (xor) by continuing
the protocol begun above- parties 2 and 3 can share their secrets
in the same fashion:
\begin{verbatimtab}
v[1,s2] := flip[2,1] xor flip[2,s2] xor s[2,1];
v[3,s2] := flip[2,1];

v[1,s3] := flip[3,1] xor flip[3,s3] xor s[3,1];
v[2,s3] := flip[3,1];
\end{verbatimtab}
Then, assuming that party 0 is the ``public party'', each party sums
its own shares, and then the sum of sum of shares is revealed
in the output view $\vx{0}{output}$. By additive homomorphism of
$\ttt{xor}$, this output is the sum of the 3 secrets, but
the protocol reveals nothing to the adversary, even if one
(or even two, in fact) of $\{1,2,3\}$ are corrupt. 
\begin{verbatimtab}
v[0,ss1] := v[1,s2] xor v[1,s3] xor flip[1,s1];
v[0,ss2] := v[2,s1] xor v[2,s3] xor flip[2,s2];
v[0,ss3] := v[3,s1] xor v[3,s2] xor flip[3,s3];

v[0,output] := v[0,ss1] xor v[0,ss2] xor v[0,ss3]
\end{verbatimtab}

Because this protocol correctly implements 3-party addition in the
binary field, it can reveal information to the adversary. For example,
suppose that $1 \in C$, and $\sx{1}{1}$ is $1$, and after running the
protocol suppose that $\vx{0}{output}$ is 0. Then the adversary knows
that 2 and 3's secrets are either 1 and 0, or 0 and 1, with 50/50
probability, and definitely neither 0 and 0, nor 1 and 1. However, the
protocol does not reveal anything more through adversarial views than
what the output reveals.
\end{example}
